---
title: "GH_test"
author: "Jennifer Schmidt"
date: "May 18, 2018"
output: html_document
---

data to download https://knb.ecoinformatics.org/knb/d1/mn/v2/object/knb.92020.1

```{r}
suppressPackageStartupMessages({
  library(leaflet)
  library(dplyr)
  library(tidyr)
  library(ggplot2)
  library(DT)
})
```

data to object
```{r}
esc <- read.csv("data/escapement_counts.csv", stringsAsFactors = FALSE)
```

```{r}
#esc <- read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/knb.92020.1", method = "libcurl"), 
#                stringsAsFactors = FALSE)
```

```{r}
median_esc <- esc %>% 
  separate(sampleDate, c("Year", "Month", "Day"), sep = "-") %>% 
  group_by(Species, SASAP.Region, Year, Location) %>% 
  summarize(escapement = sum(DailyCount)) %>% 
  group_by(Species) %>% 
  summarize(median_escapement = median(escapement))

ggplot(median_esc, aes(Species, median_escapement)) +
  geom_col() +
  coord_flip()
```

Calculate median annual escapement by species using the dplyr package Let’s convert the escapement data into a table of just the unique locations:


```{r}
locations <- esc %>% 
  distinct(Location, Latitude, Longitude) %>% 
  drop_na()
```
And display it as an interactive table:
```{r}
datatable(locations)
```
Then making a leaflet map is (generally) only a couple of lines of code:
```{r}
leaflet(locations) %>% 
  addTiles() %>% 
  addMarkers(~ Longitude, ~ Latitude, popup = ~ Location)
```
  
When you knit and view the results of this cell locally (on your own computer), you will see a map with icons marking the locations. However, when you push the html to GitHub and view your page there, you’ll see a map with no icons (as of the date of this training). This appears to be due to a certificate issue with server that provides the leaflet icons. There is a workaround, but it adds several more lines of code

# Use a custom marker so Leaflet doesn't try to grab the marker images from 
# its CDN (this was brought up in 
# https://github.com/NCEAS/sasap-training/issues/22)

```{r}
markerIcon <- makeIcon(
  iconUrl = "https://cdnjs.cloudflare.com/ajax/libs/leaflet/1.3.1/images/marker-icon.png",
  iconWidth = 25, iconHeight = 41,
  iconAnchorX = 12, iconAnchorY = 41,
  shadowUrl = "https://cdnjs.cloudflare.com/ajax/libs/leaflet/1.3.1/images/marker-shadow.png",
  shadowWidth = 41, shadowHeight = 41,
  shadowAnchorX = 13, shadowAnchorY = 41
)

leaflet(locations) %>% 
  addTiles() %>% 
  addMarkers(~ Longitude, ~ Latitude, popup = ~ Location, icon = markerIcon)
  
```
  
Do you see all those points way over in Russia? This is an Alaskan data set. Those aren’t supposed to be there. Can you guess why they’re showing up over there? If you glance through the coordinates in the locations table above it should become obvious. Here’s how to fix it:


```{r}
locs <- locations %>% mutate(Longitude = abs(Longitude) * -1)

leaflet(locs) %>% 
  addTiles() %>% 
  addMarkers(~ Longitude, ~ Latitude, popup = ~ Location, icon = markerIcon)
  
```
  
  